Strings functions analysis

### 2022-08-28 article.tex
refs changed
table for methods existing separated

    Below in section \ref{table 1} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.

@@

    \label{table 1}

    \begin{table*}
        \begin{tabular}{lllllllllllllll}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            & \begin{sideways}Popularity\end{sideways}
            & \begin{sideways}Mutual usages\end{sideways}
            & \begin{sideways}Mutable O(?)\end{sideways}
            & \begin{sideways}Immutable O(?)\end{sideways}
            \\ \hline

            capitalize &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            Get \textbf{char-at} a given position &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            compare &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            compare-ignore-case &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            concatenate &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            containts &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            count &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            ends-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            equals &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            find-first &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            find-last &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            format &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            hash &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            insert &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-alphabetic &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-empty &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            is-hexadecimal &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            is-whitespace &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            join &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            length &  &  &  &  &  &  &  &  &  &  &  &  & 1 & 1 \\

            matches-regexp &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            partition &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            repeat &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            replace-all &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            replace-first &  &  &  &  &  &  &  &  &  &   &  &  &  & \\

            split &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            starts-with &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            strip &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            substring &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\

            swap-case &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-float &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-int &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-lowercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            to-uppercase &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            trim-left &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            trim-right &  &  &  &  &  &  &  &  &  &  &  &  & n & n \\

            reverse &  &  &  &  &  &  &  &  &  &  &  &  & n & 1 \\

            remove &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            uncapitalize &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            as-bytes &  &  &  &  &  &  &  &  &  &  &  &  &  & \\

            chop &  &  &  &  &  &  &  &  &  &  &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions criteria}
        \label{tab:my_label}
    \end{table*}

>>>>

    Below in section \ref{tab:my_label} is a table with the results - metrics. It is important to note that these results take into account the methods of languages from their standard libraries.

@@

    \subsection{The table of functions in languages}

    \begin{table*}
        \begin{tabular}{lllllllllll}
            \hline
            & \begin{sideways}Java\end{sideways}
            & \begin{sideways}Ruby\end{sideways}
            & \begin{sideways}Python\end{sideways}
            & \begin{sideways}C++\end{sideways}
            & \begin{sideways}JavaScript\end{sideways}
            & \begin{sideways}Go\end{sideways}
            & \begin{sideways}C\#\end{sideways}
            & \begin{sideways}Swift\end{sideways}
            & \begin{sideways}PHP\end{sideways}
            & \begin{sideways}Rust\end{sideways}
            \\ \hline

            capitalize &  &  &  &  &  & &  &  & 1 & 1 \\

            Get \textbf{char-at} a given position &  &  &  &  &  & &  &  & 1 & 1 \\

            compare &  &  &  &  &  & &  &  & n & n \\

            compare-ignore-case &  &  &  &  &  & &  &  &  & \\

            concatenate &  &  &  &  &  & &  &  & n & n \\

            containts &  &  &  &  &  & &  &  & n & n \\

            count &  &  &  &  &  & &  &  &  & \\

            ends-with &  &  &  &  &  & &  &  & n & n \\

            equals &  &  &  &  &  & &  &  & n & n \\

            find-first &  &  &  &  &  & &  &  & n & n \\

            find-last &  &  &  &  &  & &  &  & n & n \\

            format &  &  &  &  &  & &  &  & n & n \\

            hash &  &  &  &  &  & &  &  & n & n \\

            insert &  &  &  &  &  & &  &  & n & n \\

            is-alphabetic &  &  &  &  &  & &  &  & n & n \\

            is-empty &  &  &  &  &  & &  &  & 1 & 1 \\

            is-hexadecimal &  &  &  &  &  & &  &  & n & n \\

            is-int &  &  &  &  &  & &  &  & n & n \\

            is-lowercase &  &  &  &  &  & &  &  & n & n \\

            is-uppercase &  &  &  &  &  & &  &  & n & n \\

            is-whitespace &  &  &  &  &  & &  &  & n & n \\

            join &  &  &  &  &  & &  &  & n & n \\

            length &  &  &  &  &  & &  &  & 1 & 1 \\

            matches-regexp &  &  &  &  &  & &  &  & n & n \\

            partition &  &  &  &  &  & &  &  & n & n \\

            repeat &  &  &  &  &  & &  &  & n & n \\

            replace-all &  &  &  &  &  & &  &  & n & n \\

            replace-first &  &  &  &  &  &  &  &  &  & \\

            split &  &  &  &  &  & &  &  & n & n \\

            starts-with &  &  &  &  &  & &  &  & n & n \\

            strip &  &  &  &  &  & &  &  & n & n \\

            substring &  &  &  &  &  & &  &  & n & 1 \\

            swap-case &  &  &  &  &  & &  &  & n & n \\

            to-float &  &  &  &  &  & &  &  & n & n \\

            to-int &  &  &  &  &  & &  &  & n & n \\

            to-lowercase &  &  &  &  &  & &  &  & n & n \\

            to-uppercase &  &  &  &  &  & &  &  & n & n \\

            trim-left &  &  &  &  &  & &  &  & n & n \\

            trim-right &  &  &  &  &  & &  &  & n & n \\

            reverse &  &  &  &  &  & &  &  & n & 1 \\

            remove &  &  &  &  &  & &  &  &  & \\

            uncapitalize &  &  &  &  &  & &  &  &  & \\

            as-bytes &  &  &  &  &  & &  &  &  & \\

            chop &  &  &  &  &  & &  &  &  & \\ \hline
        \end{tabular}
        \caption{String functions criteria}
        \label{tab:my_label}
    \end{table*}
